%ABSTRACT
\vspace*{0.6cm}
\begin{center}
    \fontsize{16}{19}\selectfont
    \textbf{ABSTRACT}\\[0.5cm]
\end{center}

\vspace{1cm}
{
\fontsize{12}{14}\selectfont
\noindent
This project presents the development of a Smart Water Level Monitoring System using Internet of Things (IoT) technology to address the global challenges of water scarcity and resource management. The system provides real-time water level monitoring in tanks, reservoirs, or other storage facilities, ensuring efficient water usage. It employs an ultrasonic sensor to measure water levels, which are processed by a microcontroller and displayed on a 0.96$^{\prime\prime}$ OLED screen for visual representation. Additionally, the system integrates Blynk technology, allowing users to access real-time information on their mobile devices.\\

\noindent
Key electronic components such as 1k resistors, BC547 NPN transistors, LEDs,push buttons, and a 5V DC buzzer enable various functionalities, including current limiting, signal amplification, visual indicators, manual control, and auditory alerts for critical water levels. An optional AC to DC converter ensures stable power supply for continuous operation. The system's push buttons offer customizable control, and the combination of visual and auditory cues helps prevent overflow and alert users when water levels fall below a critical thresh- old, enabling proactive water management. \\

\noindent
Testing results demonstrate the system's effectiveness in detecting high and low water levels and providing timely alerts to users. Its real-time monitoring and alerting capabilities reduce the risk of water shortages or overflows, contributing to sustainable water management. This cost-effective solution is adaptable to a variety of applications, from small household water tanks to large industrial reservoirs, making it particularly useful in regions facing water scarcity. The system's autonomous operation, low maintenance, and scalability further enhance its utility in residential, agricultural, and industrial sectors.\\

\vspace{3cm}
\noindent
Keywords: IoT, Smart Water Monitoring, Ultrasonic Sensor, Blynk Technology, Water Resource Management.

} 