%ACKNOWLEDGEMENT
\vspace*{0.6cm}
\begin{center}
    \fontsize{16}{19}\selectfont
    \textbf{ACKOWLEDGEMENT}\\[0.5cm]
\end{center}

\vspace{1cm}
%\setstretch{2.0}
{
\fontsize{12}{14}\selectfont
\noindent
We would like to express our sincere gratitude to our \textbf{Head of Department} and \textbf{Guide}, \textbf{Dr. Hanjabam Saratchandra Sharma}, for his invaluable guidance and support throughout the course of this project. His expertise, encouragement, and constructive feedback were instrumental in shaping our understanding of IoT technology and its applications. \\

\noindent
His unwavering commitment to our success and his dedication to fostering a collaborative learning environment have greatly inspired us. We are especially thankful for the time he devoted to mentoring us, answering our queries, and providing insightful suggestions that enhanced our project significantly. His ability to simplify complex concepts allowed us to grasp the intricacies of the subject matter and apply them effectively. \\

\noindent
We would also like to acknowledge the valuable resources and facilities that enabled us to conduct our research and development efficiently. The access to advanced tools and technologies played a crucial role in the successful execution of our project, allowing us to implement our ideas with precision and confidence. \\

\noindent
Finally, we express our gratitude to all individuals who participated in the testing and evaluation of the system. Their valuable feedback helped us refine the system and ensure its functionality and user-friendliness. 

\vspace{2cm}
\noindent
\begin{minipage}[t]{0.45\textwidth} % Left side for Date and Place
    \begin{flushleft}
        Date: January 21, 2025\\
        Place: Imphal
    \end{flushleft}
\end{minipage}%
\hfill % Fills the space between the minipages
\begin{minipage}[t]{0.55\textwidth} % Right side for the name and registration info
    \begin{flushright}
            Sincerly,\\
            Naorem Diyabarta Singh\\
            Ricky Thoudam\\
            Naoroibam Lanngamba Luwang\\
    \end{flushright}
\end{minipage}
} 