\section*{APPENDIX B : Calibration and Setup Guide}
\vspace*{0.6cm}
{\fontsize{12}{14}\selectfont{

    \begin{enumerate}
    \item \textbf{Hardware Setup:}
    \begin{itemize}
        \item \textbf{Components Required:}
        \begin{itemize}
            \item ESP8266 (e.g., NodeMCU)
            \item Ultrasonic sensor (HC-SR04)
            \item OLED display (SH1106)
            \item Buzzer
            \item Jumper wires
            \item Power supply (USB or battery)
            \item Water tank for testing
        \end{itemize}
        \item \textbf{Connections:}
        \begin{itemize}
            \item \textbf{Ultrasonic Sensor (HC-SR04):}
            \begin{itemize}
                \item Trig pin $\rightarrow$ GPIO14 (D5)
                \item Echo pin $\rightarrow$ GPIO12 (D6)
                \item VCC $\rightarrow$ 5V
                \item GND $\rightarrow$ GND
            \end{itemize}
            \item \textbf{OLED Display (SH1106):}
            \begin{itemize}
                \item SDA $\rightarrow$ D2 (I2C Data)
                \item SCL $\rightarrow$ D1 (I2C Clock)
                \item VCC $\rightarrow$ 3.3V
                \item GND $\rightarrow$ GND
            \end{itemize}
            \item \textbf{Buzzer:}
            \begin{itemize}
                \item Positive terminal $\rightarrow$ GPIO2 (D4)
                \item Negative terminal $\rightarrow$ GND
            \end{itemize}
        \end{itemize}
        \item \textbf{Powering the Circuit:}
        \begin{itemize}
            \item Ensure the ESP8266 is powered via USB or a 3.3V battery source.
            \item Verify all connections before powering on.
        \end{itemize}
    \end{itemize}
    
    \item \textbf{Software Configuration:}
    \begin{itemize}
        \item Install Arduino IDE:
        \begin{itemize}
            \item Download and install the Arduino IDE from \url{https://www.arduino.cc/}.
        \end{itemize}
        \item Install Necessary Libraries:
        \begin{enumerate}
            \item Open the Arduino IDE.
            \item Navigate to \textbf{Sketch > Include Library > Manage Libraries}.
            \item Search for and install:
            \begin{itemize}
                \item \texttt{Blynk}
                \item \texttt{Adafruit GFX Library}
                \item \texttt{Adafruit SH110X}
            \end{itemize}
        \end{enumerate}
        \item Set Up Blynk:
        \begin{enumerate}
            \item Create a new project in the Blynk app.
            \item Select the device as \textbf{ESP8266} and connection type as \textbf{WiFi}.
            \item Note the Auth Token provided and replace it in the code.
        \end{enumerate}
        \item Configure WiFi Credentials:
        \begin{itemize}
            \item Replace the placeholders for SSID and password in the code:
            \begin{verbatim}
            char ssid[] = "YourWiFiName";
            char pass[] = "YourWiFiPassword";
            \end{verbatim}
        \end{itemize}
        \item Upload the Code:
        \begin{enumerate}
            \item Select the board as \textbf{NodeMCU 1.0} in \textbf{Tools > Board}.
            \item Select the correct COM port.
            \item Click on the upload button to flash the code onto the ESP8266.
        \end{enumerate}
    \end{itemize}
    
    \item \textbf{Calibration:}
    \begin{itemize}
        \item Tank Height:
        \begin{itemize}
            \item Measure the height of the water tank in centimeters.
            \item Replace the value of \texttt{tankHeight} in the code with the measured height.
        \end{itemize}
        \item Testing the Ultrasonic Sensor:
        \begin{itemize}
            \item Position the sensor at the top of the water tank.
            \item Measure the distance manually using a ruler and compare it with the sensor's output.
            \item Adjust placement for accurate readings.
        \end{itemize}
    \end{itemize}
    
    \item \textbf{Testing and Validation:}
    \begin{itemize}
        \item OLED Display:
        \begin{itemize}
            \item Ensure the display shows the water level in percentage.
            \item Adjust the screen connections if it remains blank.
        \end{itemize}
        \item Buzzer:
        \begin{itemize}
            \item Test the buzzer functionality by lowering the water level to trigger the threshold (\texttt{distance <= 5 cm}).
            \item Enable/disable the buzzer via the Blynk app by toggling Virtual Pin V5.
        \end{itemize}
        \item Blynk Dashboard:
        \begin{itemize}
            \item Add widgets in the Blynk app:
            \begin{itemize}
                \item Label for Virtual Pin V1 (Water Level Percentage).
                \item Label for Virtual Pin V2 (Distance in cm).
                \item Button for Virtual Pin V5 (Buzzer control).
            \end{itemize}
            \item Validate data updates in real-time.
        \end{itemize}
    \end{itemize}
    
    \item \textbf{Troubleshooting:}
    \begin{itemize}
        \item No Display on OLED:
        \begin{itemize}
            \item Verify the I2C address (\texttt{0x3c}) and connections.
            \item Ensure the \texttt{Adafruit\_SH1106} library is properly installed.
        \end{itemize}
        \item Buzzer Not Working:
        \begin{itemize}
            \item Check GPIO2 (\texttt{D4}) connections.
            \item Ensure \texttt{buzzerEnabled} is set to \texttt{true}.
        \end{itemize}
        \item Blynk Not Connecting:
        \begin{itemize}
            \item Confirm WiFi credentials and internet connectivity.
            \item Check the Auth Token in the code.
        \end{itemize}
        \item Ultrasonic Sensor Issues:
        \begin{itemize}
            \item Test the sensor separately using a simple distance measurement script.
            \item Ensure clean and unobstructed sensor placement.
        \end{itemize}
    \end{itemize}
\end{enumerate}

} 